% \begin{enumerate}
\begin{etaremune}
  \item \ME, Yi, L., \& Zhang, H. (2024). Oversampling of Costly Non-Instrumental Information in Autistic Children. Panel presentation at the International Society for Autism Research 2024 Annual Meeting.
  \item \ME, Teng. T., \& Zhang, H. (2023). Reward-Driven Superstitions in Uncontrollable Environments. Poster presentation at the Society for Neuroeconomics 21st Annual Meeting.
  \item \ME, Teng, T., \& Zhang, H. (2023). The formation of superstitions in an uncontrollable environment. Proceedings of the Annual Meeting of the Cognitive Science Society, 45. Retrieved from \\https://escholarship.org/uc/item/5fx4t61x. Poster presentation.
  \item \ME, Yi, L., \& Zhang, H. (2022). Adults with more autistic traits are more willing to pay for "useless" information. Poster presentation at International Society for Autism Research 2022 Annual Meeting.
  \item \ME, Yi, L., \& Zhang, H. (2020). Inefficient information sampling under explicit costs in children with ASD. Poster presentation at International Society for Autism Research 2020 Virtual Meeting.
  \item Song, C., Wang, Q., Xu, J., \ME, Qin, S., \& Yi, L. (2020). Baseline arousal modulates face scanning in autism spectrum disorder. Poster presentation at International Society for Autism Research 2020 Virtual Meeting.
  \item \ME, Zhang, H., Yi, L. (2018). Adults with high autistic traits are reluctant to trade accuracy for monetary reward: a probabilistic reasoning experiment. Poster presentation at International Society for Autism Research 2018 Annual Meeting.
  \item \ME, Li, P., Yi, L. (2017) Impaired Rule Learning in Social Context of Children with Autism. Poster presentation at Society for Research in Child Development 2017 Biennial Meeting.
% \end{enumerate}
\end{etaremune}

