%% start of file `template-zh.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[12pt,a4paper,sans]{moderncv}   % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv 主题
% \moderncvstyle{classic}                        % 选项参数是 ‘casual’, ‘classic’, ‘oldstyle’ 和 ’banking’
% \moderncvcolor{blue}                          % 选项参数是 ‘blue’ (默认)、‘orange’、‘green’、‘red’、‘purple’ 和 ‘grey’
\moderncvstyle{banking}
% \moderncvtheme[blue]{classic}
% \nopagenumbers{}                             % 消除注释以取消自动页码生成功能

\pagestyle{fancy}
\fancyhf{}
\fancyfoot[L]{\the\year/\the\month}
\fancyfoot[C]{\small \textit{Haoyang Lu}}
\fancyfoot[R]{\thepage}

% 字符编码
\usepackage[utf8]{inputenc}                   % 替换你正在使用的编码
% \usepackage{CJKutf8}
% \usepackage{xltxtra}
\usepackage{fontspec}
\usepackage{xunicode}
\usepackage{xeCJK}
\setmainfont{Merriweather}
\setsansfont{Source Sans 3}
% \setsansfont{Helvetica Neue-Light}
\setmonofont{Courier New}
\setCJKmainfont{Noto Serif CJK SC}
\setCJKsansfont{Noto Sans CJK SC}
\setCJKmonofont{Noto Sans Mono CJK SC}

% 调整页边距
% \usepackage[scale=0.9]{geometry}
\usepackage[margin=0.5in]{geometry}
\recomputelengths
\setlength{\hintscolumnwidth}{2cm}           % 如果你希望改变日期栏的宽度

% 对列表各项逆序编号（用于对文章进行编号）
\usepackage[itemsep=2pt]{etaremune}

% 个人信息
\name{Haoyang}{Lu}
% \title{简历题目 (可选项)}                     % 可选项、如不需要可删除本行
\address{Rm.1305, Wangkezhen Bldg., Peking University}{Beijing, China}            % 可选项、如不需要可删除本行
\phone[mobile]{+8618670332855}              % 可选项、如不需要可删除本行
% \phone[fixed]{+2~(345)~678~901}               % 可选项、如不需要可删除本行
% \phone[fax]{+3~(456)~789~012}                 % 可选项、如不需要可删除本行
\email{luhy@pku.edu.cn}                    % 可选项、如不需要可删除本行
\social[github]{hy-lu}
\social[researchgate]{Haoyang-Lu}
% \social[linkedin]{haoyang-lu}
% \homepage{www.xialongli.com}                  % 可选项、如不需要可删除本行
% \extrainfo{附加信息 (可选项)}                 % 可选项、如不需要可删除本行
% \photo[64pt][0.4pt]{picture}                  % ‘64pt’是图片必须压缩至的高度、‘0.4pt‘是图片边框的宽度 (如不需要可调节至0pt)、’picture‘ 是图片文件的名字;可选项、如不需要可删除本行
% \quote{引言(可选项)}                          % 可选项、如不需要可删除本行

% 显示索引号;仅用于在简历中使用了引言
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother

% 分类索引
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            内容
%----------------------------------------------------------------------------------
\begin{document}
% \begin{CJK}{UTF8}{gbsn}                       % 详情参阅CJK文件包
\maketitle

\section{Research interest}
\cvitem{}{I am interested in computational psychiatry in general. My research involves using the methods of computational cognitive science to understand mental disorders. In my PhD thesis, I applied these methods to investigate information sampling in autistic children. Currently, I am exploring why people develop and maintain superstitions despite encountering contradictory evidence. In the future, I hope to advance computational psychiatry research, utilizing state-of-the-art AI, including large language models, to unravel the intricaies of mental disorders and ultimately enhance therapeutic outcomes.}

\section{Employment}
\cventry{2022 -- Present}{Postdoctoral Research Fellow}{School of Psychological and Cognitive Sciences, Peking University}{}{PI: Dr. Hang Zhang}{Conduct large-scale online experiments and use computational models to investigate the cognitive processes and influencing factors involved in the formation and updating of superstitious beliefs and the relationship with clinical/personality traits.}

\section{Education}
% \cventry{years}{degree/job title}{institution/employer} {localization}{optional: grade/...}{optional: comment/job description}
\cventry{2016 -- 2022}{PhD in Integrated Life Sciences (Psychology)}{Peking University}{Beijing, China}{}{
  \begin{itemize}
    \item Dissertation Title: \emph{Inference and Decision-making in People with Autism Spectrum Disorder or Broader Autism Phenotype}
    \item Advisors: Dr. Li Yi, Dr. Hang Zhang
    \item Introduction: The core features of autism spectrum disorders (ASD) are believed to be pertinent to how individuals interact with and sample the world. Therefore, it is crucial to understand the outcome of atypical information sampling in ASD. For this interdisciplinary project, I conducted a series of studies on information sampling in both autistic children and adults with a broader autism phenotype. Using behavioral tasks, eye-tracking/pupillometry, and computational modeling, I uncovered distinct behavioral, attentional, and cognitive processes in autistic individuals compared to neurotypical people for both instrumental and non-instrumental information sampling.
  \end{itemize}
}  % 第3到第6编码可留白
\cventry{2012 -- 2016}{BSc in Psychology}{Sun Yat-Sen University}{Guangzhou, China}{}{
  \begin{itemize}
    \item GPA: 3.98/4.00
  \end{itemize}
}

% \section{Thesis}
% % %to typeset lines with a hint on the left: 
% % \cvline{leftmark}{text} or \cvitem{leftmark}{text}
% \cvitem{Title}{\emph{Inference and Decision-making in People with Autism Spectrum Disorder or Broader Autism Phenotype}}
% \cvitem{Advisors}{Li Yi, Hang Zhang}
% \cvitem{Introduction}{\small The core features of autism spectrum disorders (ASD) are believed to be pertinent to how individuals interact with and sample the world. Therefore, it is crucial to understand the outcome of atypical information sampling in ASD. In this interdisciplinary project, I worked with two advisors, Prof.Li Yi, who specializes in child psychopathology and Prof.Hang Zhang in computational cognitive science. I conducted a series of studies on information sampling in both autistic children and adults with a broader autism phenotype. Through behavioral tasks, eye-tracking/pupillometry, and computational modeling, I uncovered distinct behavioral, attentional, and cognitive processes in autistic individuals compared to neurotypical people for both instrumental and non-instrumental information sampling.}

\section{Publications}
\subsection{Preprints or under review}
\input{unpublished}
\subsection{Peer-reviewed journal articles}
\input{journal}
\subsection{Conference abstracts}
\input{conference}

\section{Research experience}
\cventry{2016 -- 2022}{Research Assistant {\small at Child Cognition Lab \& Computation and Decision Lab}}{Peking University}{Beijing, China}{}{
  \begin{itemize}
    \item Conduct a series of behavioral and eye-tracking studies on information sampling in children and adults using MATLAB and Psychtoolbox.
    \item Fit behavioral data with hierarchical Bayesian models in R and Stan.
    \item Implement ACE models to estimate the heritability of autistic traits and information sampling.
    \item Administrate standardized psychological tests and questionnaires to children and parents.
    \item Build a set of tools for eye-tracking data analysis in R, including packages for I-VT fixation filter and pupil data preprocessing.
    \item Develop a toolbox for generating reports of questionnaires and Wechsler Intelligence Scale in R.
    \item Mentor undergraduate students in data analysis and programming for a study on implicit perspective-taking.
  \end{itemize}
}
\cventry{2014 -- 2016}{Research Assistant {\small at Child Cognition Lab \& Dr. Ying Lin's Lab}}{Sun Yat-Sen University}{Guangzhou, China}{}{
  \begin{itemize}
    \item Build and train a deep autoencoder neural network to predict the Big-Five personality traits from user data of Weibo, a Chinese social media platform.
    \item Conduct experiments on social learning of distrust and deception behaviors in autistic children.
    \item Analyze children's learning with survival analysis in R.
    \item Assist behavioral coding of children's looking patterns.
  \end{itemize}
}

\section{Teaching experience}
\cventry{2018 -- 2023}{Workshop lecturer}{R for Eye-tracking Data Analysis}{Chongqing, Nanjing, Shanghai, Beijing}{}{Design and deliver a 2-day workshop for learning to use R for data analysis, particularly eye-tracking data.}
\cventry{2021 -- 2023}{Teaching assistant}{Effective Writing and Communication in Science}{Peking University}{}{Design, tutorial delivery, and marking. Also deliver a 1\textasciitilde2 hr lecture on how to do scientific data visualization.}
\cventry{2020}{Guest lecturer}{Introduction to Cognitive Modeling}{Peking University}{}{Delivery a one-hour tutorial on Reproducibility and Literate Programming in R}
\cventry{2018}{Teaching assistant}{Child Psychopathology}{Peking University}{}{Marking and organizing group projects.}
\cventry{2017}{Teaching assistant}{Topics in Autism Research}{Peking University}{}{Design, marking, and organizing class discussion.}

\section{Honors and awards}
\cvitemwithcomment{2022}{Boya Postdoctoral Fellowship}{Peking University}
\cvitemwithcomment{2022}{PKU Outstanding Graduate}{Peking University}
\cvitemwithcomment{2020}{National Scholarship for PhD Studentsd}{Peking University}
\cvitemwithcomment{2020}{Pacemaker to Merit Student}{Peking University}
\cvitemwithcomment{2019}{Merit Student}{Peking University}
\cvitemwithcomment{2016}{SYSU Outstanding Graduate}{Sun Yat-Sen University}
\cvitemwithcomment{2016}{SYSU Outstanding Undergraduate Thesis}{Sun Yat-Sen University}
\cvitemwithcomment{2013 -- 2015}{SYSU Scholarship for Outstanding Students}{Sun Yat-Sen University}
\cvitemwithcomment{2013, 2015}{National Scholarship for Undergraduate Students}{Sun Yat-Sen University}

\section{Professional membership and service}
\cvitem{Membership}{Society for Research in Child Development; International Society for Autism Research; Cognitive Science Society; Society for Neuroeconomics}
\cvitem{Reviewing}{Autism Research; Journal of Autism and Developmental Disorders; eLife; OpenMind}

\section{Professional skills and languages}
% \cvitemwithcomment{}{fNIRS, fMRI, EEG}{Beginner}
\cvitem{Research}{Eye-tracking, Hierarchical Bayesian modeling, \LaTeX}
\cvitem{Statistics}{Linear mixed model, Bayesian statistics, Generalized additive model, Machine learning methods}
\cvitem{Programming}{R, MATLAB, Stan, Python, Git}
\cvitem{Languages}{Chinese, English}

\clearpage
% \end{CJK}
\end{document}


%% 文件结尾 `template-zh.tex'.
