\newcommand{\Revision}{\textit{Under revision}}
\newcommand{\Review}{\textit{Under review}}
\newcommand{\Submitted}{\textit{Submitted}}
\newcommand{\Manuscript}{\textit{Preparing manuscript}}
\newcommand{\CS}{*} % corresponding author
\newcommand{\CF}{\textsuperscript{\#}} % co-first author
\newcommand{\ME}{\textbf{Lu, H.}}

% \CS corresponding author, \CF co-first author.

% \begin{enumerate}
\begin{etaremune}
  \item Wei, N., \ME, Wang, Q., Song, C., Yi, L. (2023). Vigilance or avoidance: How do autistic traits and social anxiety modulate attention to the eyes? Frontiers in Neuroscience, 16, 1081769.
  \item Hu, Y., Xiong, Q., Wang, Q., Song, C., Wang, D., \ME, Shi, W., Han, Y., Liu, J., Li, X., \& others. (2022). Early development of social attention in toddlers at high familial risk for autism spectrum disorder. Infant Behavior and Development, 66, 101662.
  \item Wang, Q., \ME, Feng, S., Song, C., Hu, Y., \& Yi, L. (2021). Investigating intra-individual variability of face scanning in autistic children. Autism : The International Journal of Research and Practice, 13623613211064372.
  \item Feng, S., \ME, Wang, Q., Li, T., Fang, J., Chen, L., \& Yi, L. (2021). Face-viewing patterns predict audiovisual speech integration in autistic children. Autism Research.
  \item Feng, S., \ME, Fang, J., Li, X., Yi, L., \& Chen, L. (2021). Audiovisual speech perception and its relation with temporal processing in children with and without autism. Reading and Writing, 1–22.
  \item \ME, Yi, L., \& Zhang, H. (2019). Autistic traits influence the strategic diversity of information sampling: Insights from two-stage decision models. PLoS Computational Biology, 15(12), e1006964.
  \item \ME, Li, P., Fang, J., \& Yi, L. (2019). The perceived social context modulates rule learning in autism. Journal of Autism and Developmental Disorders, 49(11), 4698–4706.
  \item Zhang, Y., Song, W., Tan, Z., Zhu, H., Wang, Y., Lam, C. M., Weng, Y., Hoi, S. P., \ME, Chan, B. S. M., \& others. (2019). Could social robots facilitate children with autism spectrum disorders in learning distrust and deception? Computers in Human Behavior, 98, 140–149.
  \item Li, T., Hu, Y., Song, C., \ME, \& Yi, L. (2018). The measurements and mechanisms of restricted and repetitive behaviors in autism spectrum disorders. Chinese Science Bulletin, 63(15), 1438–1451.
  \item Yang, Y., Tian, Y., Fang, J., \ME, Wei, K., \& Yi, L. (2017). Trust and deception in children with autism spectrum disorders: A social learning perspective. Journal of Autism and Developmental Disorders, 47(3), 615–625.

% \end{enumerate}
\end{etaremune}
