%% start of file `template-zh.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[12pt,a4paper,roman]{moderncv}   % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv 主题
% \moderncvstyle{classic}                        % 选项参数是 ‘casual’, ‘classic’, ‘oldstyle’ 和 ’banking’
% \moderncvcolor{blue}                          % 选项参数是 ‘blue’ (默认)、‘orange’、‘green’、‘red’、‘purple’ 和 ‘grey’
\moderncvstyle{banking}
% \moderncvtheme[blue]{classic}
% \nopagenumbers{}                             % 消除注释以取消自动页码生成功能

% 字符编码
\usepackage[utf8]{inputenc}                   % 替换你正在使用的编码
% \usepackage{CJKutf8}
\usepackage{xeCJK}
\setCJKmainfont{Noto Serif CJK SC}
\setCJKmonofont{Noto Sans Mono CJK SC}

% 调整页边距
% \usepackage[scale=0.85]{geometry}
\usepackage[margin=0.5in]{geometry}
\recomputelengths
\setlength{\hintscolumnwidth}{3cm}           % 如果你希望改变日期栏的宽度

% 对列表各项逆序编号（用于对文章进行编号）
\usepackage[itemsep=2pt]{etaremune}

% 个人信息
\name{Haoyang}{Lu}
% \title{简历题目 (可选项)}                     % 可选项、如不需要可删除本行
\address{Rm.1305, Wangkezhen Bldg., Peking University, Beijing}{}            % 可选项、如不需要可删除本行
\phone[mobile]{+8618670332855}              % 可选项、如不需要可删除本行
% \phone[fixed]{+2~(345)~678~901}               % 可选项、如不需要可删除本行
% \phone[fax]{+3~(456)~789~012}                 % 可选项、如不需要可删除本行
\email{luhy@pku.edu.cn}                    % 可选项、如不需要可删除本行
\social[github]{hy-lu}
\social[researchgate]{Haoyang\_Lu2}
% \social[linkedin]{haoyang-lu}
% \homepage{www.xialongli.com}                  % 可选项、如不需要可删除本行
% \extrainfo{附加信息 (可选项)}                 % 可选项、如不需要可删除本行
% \photo[64pt][0.4pt]{picture}                  % ‘64pt’是图片必须压缩至的高度、‘0.4pt‘是图片边框的宽度 (如不需要可调节至0pt)、’picture‘ 是图片文件的名字;可选项、如不需要可删除本行
% \quote{引言(可选项)}                          % 可选项、如不需要可删除本行

% 显示索引号;仅用于在简历中使用了引言
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother

% 分类索引
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            内容
%----------------------------------------------------------------------------------
\begin{document}
% \begin{CJK}{UTF8}{gbsn}                       % 详情参阅CJK文件包
\maketitle

% \cvitem{政治面貌}{共青团员}

\section{Research interest}
\cvitem{}{I am interested in computational psychiatry in general. My research involves using the methods of computational cognitive sciences to understand the cognitive mechanisms underlying the core symptoms of mental disorders. In my PhD thesis, I applied these methods to investigate the (non-)instrumental information sampling in both autistic children and neurotypical individuals. Currently, I am studying the cognitive processes involved in the formation and updating of superstitious beliefs, such as illusory control.}

\section{Employment}
\cventry{2022 -- Present}{Postdoctoral Resaerch Fellow}{School of Psychological and Cognitive Sciences, Peking University}{}{}{Advisor: Hang Zhang}

\section{Education}
% \cventry{years}{degree/job title}{institution/employer} {localization}{optional: grade/...}{optional: comment/job description}
\cventry{2016 -- 2022}{PhD in Integrated Life Sciences (Psychology)}{Peking University}{China}{}{}  % 第3到第6编码可留白
\cventry{2012 -- 2016}{BSc in Psychology}{Sun Yat-Sen University}{China}{}{}

\section{Thesis}
% %to typeset lines with a hint on the left: 
% \cvline{leftmark}{text} or \cvitem{leftmark}{text}
\cvitem{Title}{\emph{Inference and Decision-making in People with Autism Spectrum Disorder or Broader Autism Phenotype}}
\cvitem{Advisors}{Li Yi, Hang Zhang}
\cvitem{Short abstract}{\small Beyond the core symptoms of autism, such as deficits in social interaction and repetitive/stereotyped behaviors, studies have found deficits and abnormalities in other non- social functions, such as perception and learning processes. However, while previous theories on autism spectrum disorder (ASD) have tried to explain specific symptoms, none could cover the various phenomena found in research. The Bayesian framework was introduced into autism research in 2012. It attempted to unify the atypical process of perception, learning, and social cognition at all levels in terms of abnormalities in perceptual updating for the hypothesis regarding the environment. In recent years, the Bayesian theory of ASD also included active inference to address the atypicalities in ASD. The core viewpoint under this framework is that the core features of ASD are all pertinent to how individuals interact with and sample the world. Therefore, it is crucial to understand the outcome of atypical active inference. Based on this perspective, this thesis investigates one type of active inference, disambiguatory active inference in ASD by integrating behavioral experiments, eye-tracking techniques, and computational modeling.}

\section{Publications}
\subsection{Peer-reviewed journal articles}
\input{journal}
\subsection{Conference abstracts}
\input{conference}

\section{Teaching}
\cventry{2018 -- 2023}{Workshop lecturer}{R for Eye-tracking data analysis}{Chongqing, Nanjing, Shanghai, Beijing}{}{Design and deliver a 2-day workshop for learning to use R for data analysis, particularly eye-tracking data.}
\cventry{2021, 2022, 2023}{Teaching assistant}{Effective writing and communication in science}{Peking University}{}{Design, tutorial delivery, and marking. Also deliver 1~2 hr lecture on how to do scientific data visualization.}
\cventry{2020}{Guest lecturer}{Introduction to Cognitive Modeling}{Peking University}{}{Delivery a one-hour tutorial on Reproducibility and Literate Programming in R}
\cventry{2018}{Teaching assistant}{Child psychopathology}{Peking University}{}{Marking and organizing group projects.}
\cventry{2017}{Teaching assistant}{Topics in Autism Research}{Peking University}{}{Design, marking, and organizing class discussion.}

\section{Professional membership and service}
\cvitem{Membership}{Society for Research in Child Development; International Society for Autism Research; Cognitive Science Society; Society for Neuroeconomics}
\cvitem{Reviewing}{Journal of Autism and Developmental Disorders; eLife; OpenMind}

\section{Professional skills and languages}
\cvitemwithcomment{Research}{Eye-tracking}{Expert}
\cvitemwithcomment{}{fNIRS, fMRI, EEG}{Beginner}
\cvitemwithcomment{Statistics}{Bayesian statistics, Generalizaed linear mixed model, Generalized additive model}{Expert}
\cvitemwithcomment{}{Survival analysis, Structural equation models, Machine learning methods}{Proficient}
\cvitemwithcomment{Programming}{R, MATLAB, Psychotoolbox}{Expert}
\cvitemwithcomment{}{Stan, SPSS, PsychoPy/PsychoJs, Git}{Proficient}
\cvitemwithcomment{}{JAGS, Mplus, E-Prime, Visual Basic, C++, Python, LaTeX}{Intermediate}
\cvitemwithcomment{Languages}{English}{Advanced}
\cvitemwithcomment{}{Chinese}{Native}

\clearpage
% \end{CJK}
\end{document}


%% 文件结尾 `template-zh.tex'.
